Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-01 Paper.tex
Added citations for Keccak and cross-references.

%was using tabularx, but found tabu which seems more flexible, and generally better.
\usepackage{tabu}

@@

\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
%\PassOptionsToPackage{url}\g@addto@macro{\UrlBreaks}{\UrlOrds}
% info on the above command: <https://tex.stackexchange.com/posts/10419/revisions>. Note that the three preceding lines, as well as \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref} did not fix the error where if a URL breaks over a page, it shows a snippet in the header as shown here: <https://i.stack.imgur.com/tYUe2.png>. The following command did fix this error, however only because it happened to compact the text, preventing a URL from breaking over a page. If you force a URL to break over a page, the error still occurs.

@@

@@

For most functions, an uppercase letter is used, e.g. $C$, the general cost function. These may be subscripted to denote specialised variants, \eg $C_\text{\tiny SSTORE}$, the cost function for the {\tiny SSTORE} operation. For specialised and possibly externally defined functions, I may format as typewriter text, \eg the Keccak-256 hash function (as per the winning entry to the SHA-3 contest) is denoted $\texttt{KEC}$ (and generally referred to as plain Keccak). Also $\texttt{KEC512}$ is referring to the Keccak 512 hash function.

Tuples are typically denoted with an upper-case letter, \eg $T$, is used to denote an Ethereum transaction. This symbol may, if accordingly defined, be subscripted to refer to an individual component, \eg $T_\mathbf{n}$, denotes the \hyperlink{transaction nonce}{nonce of said transaction}. The form of the subscript is used to denote its type; \eg uppercase subscripts refer to tuples with subscriptable components.

@@

When considering the use of existing functions, given a function $f$, the function $f^*$ denotes a similar, element-wise version of the function mapping instead between sequences. It is formally defined in section \ref{ch:block}.

@@

The collapse function for the set of key/value pairs in the trie, $L_I^*$, is defined as the element-wise transformation of the base function $L_I$, given as:
\begin{equation}
L_I\big( (k, v) \big) \equiv \big(\texttt{\small KEC}(k), \texttt{\small RLP}(v)\big)
\end{equation}

@@

With $L_\mathbf{T}^*$ and $L_H^*$ being element-wise sequence transformations, thus:
\begin{equation}
f^*\big( (x_0, x_1, ...) \big) \equiv \big( f(x_0), f(x_1), ... \big) \quad \text{for any function} \; f
\end{equation}

@@

\subsection{Execution}
We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}
g_0 \equiv {} & \sum_{i \in T_\mathbf{i}, T_\mathbf{d}} \begin{cases} G_{\mathrm{txdatazero}} & \text{if} \quad i = 0 \\ G_{\mathrm{txdatanonzero}} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} G_{\mathrm{txcreate}} & \text{if} \quad T_\mathbf{t} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + G_{\mathrm{transaction}}
\end{align}

@@

The state database won't be forced to maintain all past state \hyperlink{trie}{trie} structures into the future. It should maintain an age for each node and eventually discard nodes that are neither recent enough nor checkpoints; checkpoints, or a set of nodes in the database that allow a particular block's state trie to be traversed, could be used to place a maximum limit on the amount of computation needed in order to retrieve any state throughout the blockchain.

@@

$G_{\mathrm{memory}}$ & 3 & This is paid for every additional word when expanding memory. \\
$G_{\mathrm{txcreate}}$ & 32000 & This is paid by all contract-creating transactions after the {\it Homestead transition}.\\
$G_{\mathrm{txdatazero}}$ & 4 & This is paid for every zero byte of data or code for a transaction. \\
$G_{\mathrm{txdatanonzero}}$ & 68 & This is paid for every non-zero byte of data or code for a transaction. \\
$G_{\mathrm{transaction}}$ & 21000 & This is paid for every transaction. \\

@@

&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{s}[\boldsymbol{\mu}_\mathbf{s}[0]]$ \\

@@

&&&& $\boldsymbol{\sigma}'[I_\mathbf{a}]_\mathbf{s}[ \boldsymbol{\mu}_\mathbf{s}[0] ] \equiv \boldsymbol{\mu}_\mathbf{s}[1] $ \hypertarget{C tiny SSTORE}{}\\

@@

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabularx}{\textwidth}{lcX}
\toprule
Symbol & Latex Command & Description \\
\midrule
\hypertarget{bigvee}{
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements. More information is here: \cite{LatticeOrder}.}\\
\bottomrule
\end{tabularx}

>>>>

% Tabu seems more flexible, and generally better.
\usepackage{tabu}

@@

\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

% info on the above command: <https://tex.stackexchange.com/posts/10419/revisions>. Note that the three preceding lines, as well as \PassOptionsToPackage{hyphens}{url}\usepackage{hyperref} did not fix the error where if a URL breaks over a page, it shows a snippet in the header as shown here: <https://i.stack.imgur.com/tYUe2.png>. The following command did fix this error, however only because it happened to compact the text, preventing a URL from breaking over a page. If you force a URL to break over a page, the error still occurs.

@@

\usepackage[utf8]{inputenc}

@@

For most functions, an uppercase letter is used, e.g. $C$, the general cost function. These may be subscripted to denote specialised variants, \eg \hyperlink{C tiny SSTORE}{$C_\text{\tiny SSTORE}$}, the cost function for the \hyperlink{SSTORE}{\tiny SSTORE} operation. For specialised and possibly externally defined functions, I may format as typewriter text, \eg the Keccak-256 hash function (as per the winning entry to the SHA-3 contest, rather than later releases (\cite{Keccak}, \cite{KeccakWikipedia})) is denoted $\texttt{KEC}$ (and generally referred to as plain Keccak). Also $\texttt{KEC512}$ is referring to the Keccak 512 hash function.

Tuples are typically denoted with an upper-case letter, \eg $T$, is used to denote an Ethereum transaction. This symbol may, if accordingly defined, be subscripted to refer to an individual component, \eg  \hyperlink{transaction nonce}{$T_\mathbf{n}$, denotes the nonce of said transaction}. The form of the subscript is used to denote its type; \eg uppercase subscripts refer to tuples with subscriptable components.

@@

When considering the use of existing functions, given a function $f$, the function \hyperlink{f*}{$f^*$} denotes a similar, element-wise version of the function mapping instead between sequences.

@@

The collapse function for the set of key/value pairs in the trie, $L_I^*$, is defined as the \hyperlink{f*}{element-wise transformation} of the base function $L_I$, given as:
\begin{equation}
L_I\big( (k, v) \big) \equiv \big(\texttt{\small KEC}(k), \texttt{\small RLP}(v)\big)
\end{equation}

@@

\hypertarget{f*}{
With $L_\mathbf{T}^*$ and $L_H^*$ being element-wise sequence transformations, thus:
\begin{equation}
f^*\big( (x_0, x_1, ...) \big) \equiv \big( f(x_0), f(x_1), ... \big) \quad \text{for any function} \; f
\end{equation}}

@@

\subsection{Execution}
We define intrinsic gas $g_0$, the amount of gas this transaction requires to be paid prior to execution, as follows:
\begin{align}\hypertarget{g0}{
g_0 \equiv {} & \sum_{i \in T_\mathbf{i}, T_\mathbf{d}} \begin{cases} \hyperlink{Gtxdatazero}{G_{\mathrm{txdatazero}}} & \text{if} \quad i = 0 \\ \hyperlink{Gtxdatanonzero}{G_{\mathrm{txdatanonzero}}} & \text{otherwise} \end{cases} \\
{} & + \begin{cases} \hyperlink{Gtxcreate}{G_{\mathrm{txcreate}}} & \text{if} \quad T_\mathbf{t} = \varnothing \\ 0 & \text{otherwise} \end{cases} \\
{} & + \hyperlink{Gtransaction}{G_{\mathrm{transaction}}}
}\end{align}

@@

The state database won't be forced to maintain all past state \hyperlink{trie}{trie} structures into the future. It should maintain an age for each node and eventually discard nodes that are neither recent enough nor checkpoints. Checkpoints, or a set of nodes in the database that allow a particular block's state trie to be traversed, could be used to place a maximum limit on the amount of computation needed in order to retrieve any state throughout the blockchain.

@@

$G_{\mathrm{memory}}$ & 3 & This is paid for every additional word when expanding memory. \hypertarget{txcreate}{\\
$G_{\mathrm{txcreate}}$ & 32000 & This is paid by all contract-creating transactions after the {\it Homestead transition}.}\hypertarget{Gtxdatazero}{\\
$G_{\mathrm{txdatazero}}$ & 4 & This is paid for every zero byte of data or code for a transaction.}\hypertarget{Gtxdatanonzero}{ \\
$G_{\mathrm{txdatanonzero}}$ & 68 & This is paid for every non-zero byte of data or code for a transaction.}\hypertarget{Gtransaction}{ \\
$G_{\mathrm{Gtransaction}}$ & 21000 & This is paid for every transaction.} \\

@@

&&&& $\boldsymbol{\mu}'_\mathbf{s}[0] \equiv \boldsymbol{\sigma}[I_\mathbf{a}]_\mathbf{s}[\boldsymbol{\mu}_\mathbf{s}[0]]$ \hypertarget{SSTORE}{\\

@@

&&&& $\boldsymbol{\sigma}'[I_\mathbf{a}]_\mathbf{s}[ \boldsymbol{\mu}_\mathbf{s}[0] ] \equiv \boldsymbol{\mu}_\mathbf{s}[1] $ \hypertarget{C tiny SSTORE}{\\

@@

\end{cases}$ }\\

@@

\section{List of mathematical symbols}\label{app:symbols}
\begin{tabularx}{\textwidth}{lcX}
\toprule
Symbol & Latex Command & Description \\
\midrule
\hypertarget{bigvee}{
$\bigvee$ & \verb|\bigvee| & This is the least upper bound, supremum, or join of all elements operated on. Thus it is the greatest element of such elements (\cite{LatticeOrder}).}\\
\bottomrule
\end{tabularx}
